Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-04-03 doc/manuscript_hkk_drought_sensitivity.Rmd
updated with word counts etc

**Number of Words in Abstract:**  
**Number of Words in Main Text:**  
**Number of References:**  
**Number of Figures:** 5  
**Number of Tables:** 1  
**Number of Text boxes:** 0

>>>>

**Number of Words in Abstract:** 173  
**Number of Words in Main Text:** 4989  
**Number of References:** 46 
**Number of Figures:** 5  
**Number of Tables:** 1  
**Number of Text boxes:** 0
